### 2020-07-10 paper.Rmd
some notes on writing

In this paper, I present a simple extension of the k-means objective 
function that ensures when maximizing the criterion, not only the means
but also the variances become similar between groups. Hence, this paper 
is more concerned with the goal of forming similar groups, rather than 
maximizing within-group heterogeneity.

@@

## K-Means criterion

@@

---

@@

# Stuff

New objective seems to work best when N is high relative to K; 
optimizing two objectives at the same time is hard when N is low. Easier 
when only optimizing one objective (i.e., the mean, as done by normal
k-means anticlustering).

@@

# Weighted k-means

Using variable weighting (see Steinley, 2006, p. 13), we can 
adjust the relative importance of minimizing differences in means
and variances. Standard in `anticlust`: Equal weight, this is 
achieved by first creating the new variables, representing 
the squared differences from the mean, and then standardizing
the entire feature matrix. If $N$ is large enough (relative to $K$),
there is usually no need for weighting.

# Simulation

- show that k-variance anticlustering outperforms other objectives

@@

# Combined approach better than k-variance alone

>>>>

In this paper, I present a simple extension of the k-means objective 
function to maximize simililarity with regard to means and variances 
at the same time.

@@

## K-Means objective

@@

## K-variances

@@

## Bicriterion optimization model

- formalize the weighted-sum objective and use the weighted-sum method.
works well on this specific problem [although in general there are 
caveats to the weighted-sum method, see @brusco2019]. is fast, good 
results. in fact, the objectives seem to work well together (optimizing 
k-means extended often yields more similar variances than just 
k-variances!!!)

- In this paper: Formalization of the objective function, recognition
that this formulation does not change the basic structure of the k-means
objective, because it reduces to augmentation of the data input

- not interested in the Pareto efficient set! Because: Overall 
similarity should be maximized, which requires that both criteria are 
satisfied to a strong degree (not interested in just maximizing 
similarity wrt variance; this may be interesting in other applications). 
Instead: A tradeoff is possible, and in many cases, simultaneous 
optimization will meet both criteria almost as well as optimizing just
either criterion. To justify this approach: show the pareto front, which 
is not a diagonal / circle [see @brusco2012] but a RIGHT TRIANGLE! (this 
is probably because this is *anti*clustering!)

- Evaluation will consist of a comparison of different objectives based 
on the same (simple) exchange algorithm

- Future research: Application of more sophisticated bicriterion 
optimization algorithms are interesting

- How to select weights? (Oftentimes: for equal weights, the results 
are good)

- Standardization of the extended data matrix to ensure that the two
criterion functions do no differ markedly in scale [@brusco2019]

- Using variable weighting (see Steinley, 2006, p. 13), we can 
adjust the relative importance of minimizing differences in means
and variances. Standard in `anticlust`: Equal weight, this is 
achieved by first creating the new variables, representing 
the squared differences from the mean, and then standardizing
the entire feature matrix. If $N$ is large enough (relative to $K$),
there is usually no need for weighting.

# Evaluation

- Do simulations to show that k-variance anticlustering outperforms 
other objectives with regard to similarity in means / variances

- New objective seems to work best when N is high relative to K; 
optimizing two objectives at the same time is hard when N is low. Easier 
when only optimizing one objective (i.e., the mean, as done by normal
k-means anticlustering).

@@

@@
